Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-29 second-draft/pnas-word-order-si.tex
code

@@

\textcolor{red}{parseability vs parsability}

@@

\paragraph{Other Greenberg Universals}
Greenberg~\cite{greenberg1963universals} stated a total of 45 universals.
Twenty of these concern the structure of individual words (as opposed to word order, which we focus on here), and many of those have been argued to be explained by the ``dual pressures'' idea \cite{haspelmath2006against}.
The other 25 universals concern word order; Dryer \cite{dryer1992greenbergian} reformulated most of these as correlations with verb-object order; these form the basis of our formalization in Table~\ref{table:greenberg-dryer}. %, finding 16 correlations to likely be universal.
%Excluding universals not annotated in available databases, and merging some that can only be tested together we arrived at the eight correlations shown in Table~\ref{table:greenberg-dryer}.
%Testing efficiency on the excluded correlations would be feasible with additional annotation of data.
%For instance, one of these could be tested by labeling the existing databases for the distinction between manner adverbs from other kinds of adverbs.
%For another one, it would be necessary to annotate databases for additional languages that have independent plural markers (e.g., Hawaiian).
There are a few other well-supported word order universals that are not correlations with verb-object order.
This includes dominance principles~\cite{croft2003typology} such as the strong preference for subjects to precede objects.
Furthermore, there has been interest in Greenberg's universals 18 and 20, which describe correlations not with verb-object order, but of different elements of noun phrases~\cite{cinque2005deriving, culbertson2014language, dryer2018order}.
Future work should examine whether these universals can also be linked to efficiency optimization.

@@

Here we discuss how our formalization of communicative efficiency relates to other information-theoretic work on language.
Our formalization of efficiency is based on the function proposed in \cite{ferreri2003least,ferrericancho2007global,futrell2017memory,peloquin2019interactions} as a general efficiency metric for communicative systems.
The key idea is to maximize the \key{amount of information} that linguistic forms provide about meanings, while constraining \key{complexity and diversity} of forms. %; there are some differences in the formalization of complexity.
Formally, if $S$ denotes signals (e.g., words, sentences) and $R$ denotes their referents (e.g., objects in a reference game), then this efficiency metric takes the form (notation slightly varies across these publications):
\begin{equation}\label{eq:eff-general}
I[S, R] - \lambda H[S]
\end{equation}
where $I[S, R]$ describes the \key{informativity} of the signals $S$ about their referents $R$, and $H[S]$ describes the \key{complexity} of the communication system.
While prior studies \cite{ferreri2003least, kemp2012kinship,regier2015word,zaslavsky2018efficient} mostly considered settings where the signals $S$ are individual words without further structure, the signals are entire sentences $\mathcal{U}$ in our setting.
The underlying messages $R$ which the speaker aims to convey are the syntactic structures $\mathcal{T}$.
By the principle of compositionality \cite{frege1892sinn}, the meaning of a sentence is a function of the meanings of the parts and how they are combined.
The syntactic structure specifies how the meanings of words are combined; therefore, recovering the syntactic structure is a prerequisite to understanding a sentence correctly.
%The idea that efficient languages will permit the listener to infer grammati

We therefore arrive at the following efficiency metric:
\begin{equation}\label{eq:efficiency}
	R_{\textit{Eff}} := R_{\textit{Parseability}} + \lambda R_\textit{Pred}
\end{equation}
where \key{parseability} is the amount of information that utterances provide about their underlying syntactic structures:
\begin{equation}
	R_{Pars} := I[\mathcal{U},\mathcal{T}] = \sum_{t,u} p(t,u) \log \frac{p(t|u)}{p(t)}
\end{equation}
and \key{predictability} is the negative entropy or surprisal of the language:
\begin{equation}
	R_{Pred} := - H[\mathcal{U}] = \sum_{u} p(u) \log p(u)
\end{equation}
This efficiency metric~(\ref{eq:eff-general}) is also equivalent to a deterministic version \cite{strouse2017deterministic} of the Information Bottleneck approach, which has been successfully applied to modeling word meaning across different domains \cite{zaslavsky2018efficient, zaslavsky2019semantic}.
The Information Bottleneck models complexity using a mutual information term instead of the entropy.
This mutual information formalization is appropriate to codes that are nondeterministic \cite{zaslavsky2018efficient}.
As we assume deterministic grammars that transduce every underlying syntactic structure into one surface order, our model corresponds to the Deterministic Information Bottleneck~\cite{strouse2017deterministic}, which arises when the encoder is deterministic, and which uses the entropy as the complexity measure.
Entropy also arises naturally as a complexity measure from the role played by surprisal in determining human language processing effort~\cite{hale2001probabilistic,levy2008expectation,smith2013effect}.

@@

In the efficiency objective
\begin{equation}\label{eq:efficiency}
	R_{\textit{Eff}} := R_{\textit{Pars}} + \lambda R_\textit{Pred}
\end{equation}
the value of $\lambda$ is constrained to be in $[0,1)$.
This means, surprisal must be weighted less strongly than parseability.

Greater values of $\lambda$ can mathematically result in degenerate solutions.
To show this, note that the following inequality always holds:
\begin{equation}
I[U; T] \leq H[U].
\end{equation}
Therefore, if $\lambda \geq 1$, the efficiency objective satisfies 
\begin{equation}
    R_{Eff} = I[U; T] - \lambda H[U] \leq 0.
\end{equation}
and it takes the maximally possible value zero if $U$ maps all trees to a single utterance, in which case both $I[U; T]$ and $H[U]$ are zero.
This is a degenerate language with only a single utterance, which is simultaneously used to convey all meanings.
While the design of our word order grammars precludes a collapse of all trees to a single utterance, this shows that an objective with $\lambda \geq 1$ cannot be a generally applicable objective for language efficiency.
In conclusion, $\lambda$ is constrained to be in $[0,1)$, with values closer to $1$ placing similar weights on both predictability and parseability, whereas values closer to $0$ diminish the role of predictability.

In our experiments, we chose $\lambda = 0.9$ as a mathematically valid value that puts similar weight on both predictability and parseability.
The computational cost of grammar optimization precluded repeating the experiment for many values of $\lambda$.
We note that each of the eight correlations is predicted by at least parseability or predictability, without any contradictory predictions (Table~\ref{tab:all-predictions-1}).
%Indeed, the same holds for all of the 38 syntactic relations in UD  (Table~\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})
%We additionally report results with $\lambda = 0$, i.e., placing all weight on parseability.
That is, at $\lambda$ close to its maximal value, the predictions of optimizing the two scoring functions individually add up to the predictions of efficiency optimization.
Small values of $\lambda$ correspond to the case where predictability plays no role, and only parseability is optimized (Table~\ref{tab:all-predictions-1}).
We also verified the robustness of our results to small variations of $\lambda$, by reporting results with $\lambda=1$ in Table~\ref{table:corr-resu-previous}.

@@

%- number of different forms 
%
%- complexity of the mapping 
%
%- MI between
%
%
%
%We model the first term as the 
% degree to which listeners can reconstruct dependency parse structures from an utterance, i.e., the \key{parseability} if the language. This is formalized as the amount of information that utterances $u$ provide about their underlying syntactic structures $t$:
%\begin{equation}
%	R_{Pars} := I[\mathcal{U},\mathcal{T}] = \sum_{t,u} p(t,u) \log \frac{p(t|u)}{p(t)}
%\end{equation}
%where the sum runs over all possible pairs of sentences $l$ and syntactic structures $t$ in the language.
%%This quantity describes the degree to which syntactic structures can be unambiguously recovered from sentences, and quantifies how successful communication is (cf. Figure~\ref{fig:comm}).
%
%
%
%We formalize the complexity of a language as its entropy~\cite{ferreri2003least,ferrericancho2007global,futrell2017memory}.
%In our setting, this corresponds to the average word-by-word surprisal, the degree to which sentences are unpredictable from the general statistics of the language.
%Surprisal has been found to be a highly accurate and general predictor of human online processing difficulty \cite{hale2001probabilistic,levy2008expectation,smith2013effect}.
%%and can be justified  in terms of predictive coding theories of information processing in the brain \cite{friston2009predictive} as well as the general algorithmic complexity of language generation and comprehension \cite{li2008introduction}.
%
%In expectation over all utterances $u$ in a language, the negative surprisal describes the \key{predictability}, or negative entropy, of the utterances:
%\begin{equation}
%	R_{Pred} := - H[\mathcal{U}] = \sum_{u} p(u) \log p(u)
%\end{equation}
%where the sum runs over all possible sentences $u$ that belong to the language.
%%In keeping with Zipf's Force of Unification, this quantity describes how homogeneous the language is, i.e., it is larger if the distribution over sentences is concentrated on a smaller number of frequent sentences. 
%
%
%
%The efficiency of a language is the weighted combination of these two scoring functions~\cite{ferreri2003least,frank2012predicting,zaslavsky2018efficient,kemp2012kinship,regier2015word,goodman2013knowledge}:
%\begin{equation}\label{eq:efficiency}
%	R_{\textit{Eff}} := R_{\textit{Parseability}} + \lambda R_\textit{Pred}
%\end{equation}
%with an interpolation weight $\lambda \in [0,1)$.
%In all results from Study 2 reported here, we set $\lambda := 0.9$ in Equation~\ref{eq:efficiency}.
%See SI appendix section 5 for mathematical discussion of $\lambda$, and robustness to other choices.
%
%

@@

\begin{table}
\small{
\begin{center}
\begin{tabular}{l||l|lll|llll|ll|llllll}
 & Prevalence & \multicolumn{3}{c|}{Bayesian} & \multicolumn{4}{c|}{Frequentist} \\ 
& & Mean & SD & $p(\beta \leq 0)$ & $\beta$ & SE & $z$ & p \\
\hline\hline
	\input{../results/correlations/output/efficiency-results-full.tex}
\end{tabular}
\end{center}
}
	\caption{Detailed results for Bayesian and Frequentist mixed-effects analyses for the eight correlations. 
We show (1) the raw prevalence of each correlation in the optimized grammars (8 grammars for each of the 51 languages),
(2) for the Bayesian analysis, we provide posterior mean and SD of $\beta$, and the posterior probability that $\beta$ has the opposite sign,
(3) for the Frequentist analysis, we provide the point estimate, SE, $z$, and $p$-values (2-sided).
The frequentist analysis confirms the results of the Bayesian analysis.
}\label{tab:corr-regression}
\end{table}

@@

\begin{table*} % TODO figure out away to make this table more aesthetic
	\begin{center}	
\includegraphics[width=0.8\textwidth]{si-table-perrel-1-1.png}
\end{center}
\caption{Predictions on UD relations with predictions from the typological literature. The first section contains the eight correlations discussed in the main paper (See Section~\ref{sec:correlations}); the second section provides other relations for which predictions are available. In the last column, we indicate what direction would be expected typologically.}
\label{tab:all-predictions-1}
\end{table*}

\footnotetext{The \emph{aux} syntactic relation in UD has the auxiliary (verb-patterner) as its dependent, and has direction \emph{opposite} to the auxiliary-verb relation \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}. Therefore, this relation is \emph{anti-correlated} with the verb-object relation, while \raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}} is \emph{correlated}.  For simplicity, we display this as a corelation in this table.}

\begin{table*} % TODO figure out away to make this table more aesthetic
	\begin{center}	
\includegraphics[width=0.8\textwidth]{si-table-perrel-2-1.png}  
\end{center}
\caption{Predictions on UD relations for which no predictions are available in the typological literature.  ``Uninterpretable'' UD relations are those which collapse so many different linguistic relationships that they are not linguistically meaningful. ``UD artifact'' relations are those whose order is determined strictly by UD parsing standards, such that their order is not linguistically meaningful: these include dependencies such as the connection between two parts of a word that have been separated by whitespace inserted as a typo (\emph{goeswith}).}
\label{tab:all-predictions-2}
\end{table*}

\subsection{Other Experiments}
In Table~\ref{table:corr-resu} we report the results of our two previous, preregistered, simulations\footnote{\url{http://aspredicted.org/blind.php?x=8gp2bt}, \url{https://aspredicted.org/blind.php?x=bg35x7}. For the results of the locality simulations, see the DLM results in Table~\ref{tab:all-predictions-1}, see also Section~\ref{sec:DLM}.} together with results from the main experiment.
These experiments all had the same setup described in Section~\ref{sec:neural-architectures}, which was fixed before starting simulations; differences are that (1) one simulation places fully equal weight on parseability and predictability ($\lambda=1.0$), and (2) the final experiment uses three random seeds per grammar.
Results across all three experiments agree; jointly optimizing grammars for parseability and predictability produces all eight correlations.

>>>>

\newcommand{\utterance}{\mathcal{U}}
\newcommand{\tree}{\mathcal{T}}

@@

\textcolor{red}{word limit}

\textcolor{red}{grammar example in SI}

\textcolor{red}{cover letter goes to broad person}

\textcolor{red}{Czech parser}

\textcolor{red}{random all 50}

@@

%\textcolor{red}{Greenberg~\cite{greenberg1963universals} stated a total of 45 universals.
%Twenty of these concern the structure of individual words (as opposed to word order, which we focus on here), and many of those have been argued to be explained by the ``dual pressures'' idea \cite{haspelmath2006against}.
%The other 25 universals concern word order; Dryer \cite{dryer1992greenbergian} reformulated most of these as correlations with verb-object order, finding 16 correlations to likely be universal.
%Excluding universals not annotated in available databases, and merging some that can only be tested together we arrived at the eight correlations shown in Table~\ref{table:corr-dryer}.
%Testing efficiency on the excluded correlations would be feasible with additional annotation of data.
%For instance, one of these could be tested by labeling the existing databases for the distinction between manner adverbs from other kinds of adverbs.
%For another one, it would be necessary to annotate databases for additional languages that have independent plural markers (e.g., Hawaiian).}

@@

Here we discuss how our formalization of communicative efficiency relates to other information-theoretic work on language.
Our formalization of efficiency is based on the function proposed in \cite{ferreri2003least,ferrericancho2007global,futrell2017memory,peloquin2019interactions} as a general efficiency metric for communicative systems.
The key idea is to maximize the \key{amount of information} that linguistic forms provide about meanings, while constraining \key{complexity and diversity} of forms. %; there are some differences in the formalization of complexity.
Formally, if $S$ denotes signals (e.g., words, sentences) and $R$ denotes their referents (e.g., objects in a reference game), then this efficiency metric takes the form (notation slightly varies across these publications):
\begin{equation}\label{eq:eff-general}
I[S, R] - \lambda H[S]
\end{equation}
where $I[S, R]$ describes the \key{informativity} of the signals $S$ about their referents $R$, and $H[S]$ describes the \key{complexity} of the communication system.
While prior studies \cite{ferreri2003least, kemp2012kinship,regier2015word,zaslavsky2018efficient} mostly considered settings where the signals $S$ are individual words without further structure, the signals are entire sentences $\utterance$ in our setting.
The underlying messages $R$ which the speaker aims to convey are the syntactic structures $\tree$.
By the principle of compositionality \cite{frege1892sinn}, the meaning of a sentence is a function of the meanings of the parts and how they are combined.
The syntactic structure specifies how the meanings of words are combined; therefore, recovering the syntactic structure is a prerequisite to understanding a sentence correctly.
%The idea that efficient languages will permit the listener to infer grammati

We therefore arrive at the following efficiency metric:
\begin{equation}\label{eq:efficiency}
	R_{\textit{Eff}} := R_{\textit{Parseability}} + \lambda R_\textit{Pred}
\end{equation}
where \key{parseability} is the amount of information that utterances provide about their underlying syntactic structures:
\begin{equation}
	R_{Pars} := I[\utterance,\tree] = \sum_{t,u} p(t,u) \log \frac{p(t|u)}{p(t)}
\end{equation}
and \key{predictability} is the negative entropy or surprisal of the language:
\begin{equation}
	R_{Pred} := - H[\utterance] = \sum_{u} p(u) \log p(u)
\end{equation}
This efficiency metric~(\ref{eq:eff-general}) is also equivalent to a deterministic version \cite{strouse2017deterministic} of the Information Bottleneck approach, which has been successfully applied to modeling word meaning across different domains \cite{zaslavsky2018efficient, zaslavsky2019semantic}.
The Information Bottleneck models complexity using a mutual information term instead of the entropy.
This mutual information formalization is appropriate to codes that are nondeterministic \cite{zaslavsky2018efficient}.
As we assume deterministic grammars that transduce every underlying syntactic structure into one surface order, our model corresponds to the Deterministic Information Bottleneck~\cite{strouse2017deterministic}, which arises when the encoder is deterministic, and which uses the entropy as the complexity measure.
Entropy also arises naturally as a complexity measure from the role played by surprisal in determining human language processing effort~\cite{hale2001probabilistic,levy2008expectation,smith2013effect}.

@@

In the efficiency objective
\begin{equation}\label{eq:efficiency}
	R_{\textit{Eff}} := R_{\textit{Pars}} + \lambda R_\textit{Pred}
\end{equation}
the value of $\lambda$ is constrained to be in $[0,1)$.
This means, surprisal must be weighted less strongly than parsability.

Greater values of $\lambda$ mathematically result in degenerate solutions.
To show this, note that the following inequality always holds:
\begin{equation}
I[\utterance; \tree] \leq H[\utterance].
\end{equation}
Therefore, if $\lambda \geq 1$, the efficiency objective satisfies 
\begin{equation}
    R_{Eff} = I[\utterance; \tree] - \lambda H[\utterance] \leq 0.
\end{equation}
and it takes the maximally possible value zero if there is only a single utterance $\utterance$, in which case both $I[\utterance; \tree]$ and $H[\utterance]$ are zero.
This is a degenerate language with only a single utterance, which is simultaneously used to convey all meanings.
While the design of our word order grammars precludes a collapse of all trees to a single utterance, this shows that an objective with $\lambda \geq 1$ cannot be a generally applicable objective for language efficiency.
In conclusion, $\lambda$ is constrained to be in $[0,1)$, with values closer to $1$ placing similar weights on both predictability and parsability, whereas values closer to $0$ diminish the role of predictability.

In our experiments, we chose $\lambda = 0.9$ as a mathematically valid value that puts similar weight on both predictability and parsability.
The computational cost of grammar optimization precluded repeating the experiment for many values of $\lambda$.
We note that each of the eight correlations is predicted by at least parseability or predictability, without any contradictory predictions (Table~\ref{tab:all-predictions-1}).
%Indeed, the same holds for all of the 38 syntactic relations in UD  (Table~\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})
%We additionally report results with $\lambda = 0$, i.e., placing all weight on parseability.
That is, at $\lambda$ close to its maximal value, the predictions of optimizing the two scoring functions individually add up to the predictions of efficiency optimization.
Small values of $\lambda$ correspond to the case where predictability plays no role, and only parseability is optimized (Table~\ref{tab:all-predictions-1}).
We also verified the robustness of our results to small variations of $\lambda$, by reporting results with $\lambda=1$ in Table~\ref{table:corr-resu}.

@@

%- number of different forms 
%
%- complexity of the mapping 
%
%- MI between
%
%
%
%We model the first term as the 
% degree to which listeners can reconstruct dependency parse structures from an utterance, i.e., the \key{parseability} if the language. This is formalized as the amount of information that utterances $u$ provide about their underlying syntactic structures $t$:
%\begin{equation}
%	R_{Pars} := I[\utterance,\tree] = \sum_{t,u} p(t,u) \log \frac{p(t|u)}{p(t)}
%\end{equation}
%where the sum runs over all possible pairs of sentences $l$ and syntactic structures $t$ in the language.
%%This quantity describes the degree to which syntactic structures can be unambiguously recovered from sentences, and quantifies how successful communication is (cf. Figure~\ref{fig:comm}).
%
%
%
%We formalize the complexity of a language as its entropy~\cite{ferreri2003least,ferrericancho2007global,futrell2017memory}.
%In our setting, this corresponds to the average word-by-word surprisal, the degree to which sentences are unpredictable from the general statistics of the language.
%Surprisal has been found to be a highly accurate and general predictor of human online processing difficulty \cite{hale2001probabilistic,levy2008expectation,smith2013effect}.
%%and can be justified  in terms of predictive coding theories of information processing in the brain \cite{friston2009predictive} as well as the general algorithmic complexity of language generation and comprehension \cite{li2008introduction}.
%
%In expectation over all utterances $u$ in a language, the negative surprisal describes the \key{predictability}, or negative entropy, of the utterances:
%\begin{equation}
%	R_{Pred} := - H[\utterance] = \sum_{u} p(u) \log p(u)
%\end{equation}
%where the sum runs over all possible sentences $u$ that belong to the language.
%%In keeping with Zipf's Force of Unification, this quantity describes how homogeneous the language is, i.e., it is larger if the distribution over sentences is concentrated on a smaller number of frequent sentences. 
%
%
%
%The efficiency of a language is the weighted combination of these two scoring functions~\cite{ferreri2003least,frank2012predicting,zaslavsky2018efficient,kemp2012kinship,regier2015word,goodman2013knowledge}:
%\begin{equation}\label{eq:efficiency}
%	R_{\textit{Eff}} := R_{\textit{Parseability}} + \lambda R_\textit{Pred}
%\end{equation}
%with an interpolation weight $\lambda \in [0,1)$.
%In all results from Study 2 reported here, we set $\lambda := 0.9$ in Equation~\ref{eq:efficiency}.
%See SI appendix section 5 for mathematical discussion of $\lambda$, and robustness to other choices.
%
%

@@

\begin{table}
\small{
\begin{center}
\begin{tabular}{l||l|lll|llll|ll|llllll}
Correlation & Prevalence & \multicolumn{3}{c}{Bayesian} & \multicolumn{4}{c}{Frequentist} \\ 
& & Mean & SD & $p(\beta \leq 0)$ & $\beta$ & SE & $z$ & p \\
\hline\hline
	\input{../results/correlations/output/efficiency-results-full.tex}
\end{tabular}
\end{center}
}
	\caption{Detailed results for Bayesian and Frequentist mixed-effects analyses for the eight correlations. 
We show (1) the raw prevalence of each correlation in the optimized grammars (8 grammars for each of the 51 languages),
(2) for the Bayesian analysis, we provide posterior mean and SD of $\beta$, and the posterior probability that $\beta$ has the opposite sign,
(3) for the Frequentist analysis, we provide the point estimate, SE, $z$, and $p$-values (2-sided).
The frequentist analysis confirms the results of the Bayesian analysis.
}\label{tab:corr-regression}
\end{table}

@@

\begin{table*} % TODO figure out away to make this table more aesthetic
	\begin{center}	
\includegraphics[width=0.8\textwidth]{si-table-perrel-1.pdf}  
\end{center}
\caption{Predictions on UD relations with predictions from the typological literature. The first section contains the eight correlations discussed in the main paper (See Section~\ref{sec:correlations}); the second section provides other relations for which predictions are available. In the last column, we indicate what direction would be expected typologically.}
\label{tab:all-predictions-1}
\end{table*}
%%posterior_perRelation_Real_conj.pdf         posterior_perRelation_Real_goeswith.pdf     posterior_perRelation_Real_nummod.pdf       
%%user@user-G751JY:~/grammar-optim/results/correlations$ evince figures/posteriors/posterior_perRelation_Real_csubj.pdf 
%%user@user-G751JY:~/grammar-optim/results/correlations$ 
%\begin{table*} % TODO figure out away to make this table more aesthetic
%	\begin{center}	
%\small{
%\begin{tabular}{l|l|l|l|ll|l|l|llllllllllllllllllllllllllll}
%	\hline
%&	Relation & Real & DLM & Pred & Pars & Efficiency & Expected Prevalence  \\ \hline
%% From Dryer	
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}&	lifted\_case  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_lifted_case.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_lifted_case.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_lifted_case.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_case.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_lifted_case.pdf} & $> 50 \%$ \citep{dryer1992greenbergian}  \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}}&	lifted\_cop  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_lifted_cop.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_lifted_cop.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_lifted_cop.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_cop.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_lifted_cop.pdf} & $> 50 \%$ \citep{dryer1992greenbergian}  \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}&	aux\footnotemark  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_aux.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_aux.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_aux.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_aux.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_aux.pdf}  & $<50\%$ \citep{dryer1992greenbergian} \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}&	nmod  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_nmod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_nmod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_nmod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_nmod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_nmod.pdf}  & $>50\%$ \citep{dryer1992greenbergian} \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}}&	acl  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_acl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_acl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_acl.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_acl.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_acl.pdf}   & $>50\%$  \citep{dryer1992greenbergian} \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {6}}}&	lifted\_mark  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_lifted_mark.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_lifted_mark.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_lifted_mark.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_mark.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_lifted_mark.pdf} & $> 50 \%$ \citep{dryer1992greenbergian}  \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {7}}}&	obl  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_obl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_obl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_obl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_obl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_obl.pdf}  & $>50\%$ \citep{dryer1992greenbergian} \\
%\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {8}}}&	xcomp  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_xcomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_xcomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_xcomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_xcomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_xcomp.pdf}  & $>50\%$ \citep{dryer1992greenbergian} \\
%%\hdashline
%\hline
%% Other universals, not in Dryer
%&advcl  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_advcl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_advcl.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_advcl.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_advcl.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_advcl.pdf}   & $>50\%$ \citep{greenberg1963universals,diessel2001ordering} \\
%&ccomp  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_ccomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_ccomp.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_ccomp.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_ccomp.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_ccomp.pdf}   & $>50\%$ (cf. \cite{dryer1980positional}) \\ % TODO According to Dryer 1980, there is a correlation
%&csubj  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_csubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_csubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_csubj.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_csubj.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_csubj.pdf}   & $>50\%$ (cf. \cite{dryer1980positional}) \\% TODO According to Dryer 1980, there is a correlation
%&nsubj  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_nsubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_nsubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_nsubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_nsubj.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_nsubj.pdf}  & See Section~\ref{sec:correlations} \\
%&amod  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_amod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_amod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_amod.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_amod.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_amod.pdf}   &  $\approx 50\%$ \citep{dryer1992greenbergian} \\
%&nummod  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Real_nummod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_DependencyLength_nummod.pdf}   &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Predictability_nummod.pdf}  &   \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_nummod.pdf}  &  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Efficiency_nummod.pdf}   &$\approx 50\%$ \citep[][89A, 83A]{wals} \\ 
% \hline
%%comp. &
%%\multirow{3}{*}{NP}&
%%	AP &
%\end{tabular}
%}
%\end{center}
%\caption{Predictions on UD relations with predictions from the typological literature. The first section contains the eight correlations discussed in the main paper (See Section~\ref{sec:correlations}); the second section provides other relations for which predictions are available. In the last column, we indicate what direction would be expected typologically.}
%\label{tab:all-predictions-1}
%\end{table*}
